### 2022-06-24 README.Rmd
Updated travis build link in README

<!-- README.md is generated from README.Rmd. Please edit that file -->
[![Build status](https://ci.appveyor.com/api/projects/status/xwu8nket2u1pd5ij?svg=true)](https://ci.appveyor.com/project/hsmith9002/diffenrich)

>>>>

<!-- README.md is generated from README.Rmd. Please edit that file -->
[![Build Status](https://app.travis-ci.com/SabaLab/diffEnrich.svg?branch=master)](https://app.travis-ci.com/SabaLab/diffEnrich)
